\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-07-31 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
Les tables sont bonnes

\begin{table}
	\input{Table1.tex}
\end{table}

>>>>

\begin{table}
	\input{Table1.tex}
		\begin{tablenotes}
		\tiny
		\item Statistics are obtained weighting each observation by its value relative to total trade flows.
		\item The additive term is expressed in fraction of fas price.
		\item For the  4-digit model, statistics for observed data have been calculated for the same set of years as used for estimation, i.e.
		1974, 1981, 1989, 2001, 2009, 2013, 2017 and 2019
		\item \textbf{Model (A): With ad-valorem transpost costs only}
		\item \textbf{Model (B): With additive and ad-valorem transport costs}
	\end{tablenotes}
\end{table}
